Dominance Regions for Imaginary $\bfg$-vectors

### 2020-08-15 dominance_regions.tex
Some notes

  Is the following result true beyond rank 2?
  \begin{lemma}
    For $\mu\in\RR^2$, $\pi_2^{-1}(\mu)$ is a translate of the imaginary cone $\cI$ or the union of such with a single point.
  \end{lemma}
  \begin{proof}
    Maybe the vertex of this cone is given by $\lambda=(\lambda_1,\lambda_2)$ where
    \[\lambda_1=\frac{2b\mu_2-4\mu_1}{bc-4+\sqrt{bc(bc-4)}} \qquad \text{and} \qquad \lambda_2=\frac{2c\mu_1-4\mu_2}{bc-4+\sqrt{bc(bc-4)}}.\]
  \end{proof}

>>>>

  Is the following result true beyond rank 2?
  \begin{lemma}
    For $\mu\in\RR^2$, $\pi_2^{-1}(\mu)$ is a translate of the imaginary cone $\cI$ or the union of such with a single point.
  \end{lemma}
  \begin{proof}
    For $\mu$ in the second quadrant, the vertex of this cone should be given by $\lambda=(\lambda_1,\lambda_2)$ where
    \[\lambda_1=\frac{2b\mu_2-4\mu_1}{bc-4+\sqrt{bc(bc-4)}} \qquad \text{and} \qquad \lambda_2=\frac{2c\mu_1-4\mu_2}{bc-4+\sqrt{bc(bc-4)}}.\]
    (This comes from setting $\mu$ to be the vertex opposite $\lambda$ inside the dominance region $\cP(\lambda)$ and then solving for $\lambda$.)
  \end{proof}
  \begin{remark}
    We want to understand what the curve is that results when we have $\mu$ lie along the unit circle, this should be possible by plugging $(\cos(\theta),\sin(\theta))$ into this formula for $\lambda$ and seeing what ellipse we get.
  \end{remark}
